\documentclass[busletter,dateno]{newlfm}
\usepackage{etoolbox}

\makeatletter
\patchcmd{\@zfancyhead}{\fancy@reset}{\f@nch@reset}{}{}
\patchcmd{\@set@em@up}{\f@ncyolh}{\f@nch@olh}{}{}
\patchcmd{\@set@em@up}{\f@ncyolh}{\f@nch@olh}{}{}
\patchcmd{\@set@em@up}{\f@ncyorh}{\f@nch@orh}{}{}
\makeatother
%\usepackage{kpfonts}
\usepackage{fontawesome}
%\usepackage{url}

\widowpenalty=1000
\clubpenalty=1000

\newlfmP{headermarginskip=20pt}
\newlfmP{sigsize=50pt}
\newlfmP{dateskipafter=20pt}
%\newlfmP{addrfromphone}
%\newlfmP{addrfromemail}
%\PhrPhone{Phone}
%\PhrEmail{Email}

\namefrom{Sachin More}
\addrfrom{\today\\[10pt]
		    141 Howard Street\\
			Northborough, MA 01532
}
%\phonefrom{+1-508-335-6351}
%\emailfrom{sachinsureshmore@gmail.com}

%\addrto{%
%Faculty Search Committee\\
%Department of Computer Science\\
%Clemson University\\
%Clemson, SC 29634-0974}

\greetto{To Whom It May Concern:}
\closeline{Sincerely,}

\begin{document}
\begin{newlfm}
Having read the description for your opening for a Senior Data Analyst,
I have determined that this position is one where I could make a positive
contribution to National Grid.  Thus, I am pleased to share my resume.

My understanding, from evaluating the responsibilities of the role and the
objectives of your company, is that my background could be helpful in
addressing your needs. Specifically, my training includes extensive experience
with Python programming and debugging skills. It has been my primary
development language for the last four years. Additionally, Linux was the
primary development platform that I used for over two decades. Moreover,
I was immersed in learning about computer system architecture and operating systems while at EMC
and Infinidat, where I was immersed in system software development work. 

Certainly, it is not just technical skills which I would bring to this role.
My background has allowed me to understand the benefits of leadership and
teamwork. It is undeniable, that I come to recognize that a willingness to
exchange new ideas is critical to development. This has been essential to my
analytical, problem-solving and decision-making skills. Indeed, these skills
were maximized when I took the initiative to identify an enterprise grade 
solid state drive to improve the performance of EMC's enterprise storage
system. As a result, EMC Corporation became the first enterprise storage
company to offer solid state disk storage. And I was honored with the EMC
President's Award.

Thank you for your consideration.  I welcome the opportunity to answer any
questions you may have. 
\end{newlfm}
\end{document}
