\documentclass[busletter,dateno]{newlfm}
\usepackage{etoolbox}
\makeatletter
\patchcmd{\@zfancyhead}{\fancy@reset}{\f@nch@reset}{}{}
\patchcmd{\@set@em@up}{\f@ncyolh}{\f@nch@olh}{}{}
\patchcmd{\@set@em@up}{\f@ncyolh}{\f@nch@olh}{}{}
\patchcmd{\@set@em@up}{\f@ncyorh}{\f@nch@orh}{}{}
\makeatother

%\usepackage{kpfonts}
\usepackage{fontawesome}
%\usepackage{url}

\widowpenalty=1000
\clubpenalty=1000

\newlfmP{headermarginskip=20pt}
\newlfmP{sigsize=50pt}
\newlfmP{dateskipafter=20pt}
\newlfmP{addrfromphone}
\newlfmP{addrfromemail}
\PhrPhone{Phone}
\PhrEmail{Email}

\namefrom{Sachin More}
\addrfrom{\today\\[10pt]
		    141 Howard Street\\
			Northborough, MA 01532
}
\phonefrom{+1-508-335-6351}
\emailfrom{sachinsureshmore@gmail.com}

%\addrto{%
%Faculty Search Committee\\
%Department of Computer Science\\
%Clemson University\\
%Clemson, SC 29634-0974}

\greetto{To Whom It May Concern:}
\closeline{Sincerely,}

\begin{document}
\begin{newlfm}
Having read the description for your opening for a Senior Software Engineer,
I have determined that this position is one where I could make a positive
contribution to Nike. Thus, I am pleased to share my resume.

My understanding, from evaluating the responsibilities of the role and the
objectives of your company, is that my background could be helpful in
addressing your needs. Specifically, my training includes experience
with Python programming language. I designed and developed the entire software
infrastructure in Python and used by the Hardware Engineering team at Infinidat Inc.
Additionally, I have used various Python
packages like pandas, matplotlib etc. that are used for data analytics. I used
these packages to create reports for the upper management. These reports
summarized data uploaded by our field installations. The data, stored in our internal
database system, was accessed using a REST API. I have
several certifications in the field of data analytics for courses designed by IBM.
I am also conversant with Matlab/Octave and have completed the Matlab Onramp
certification. Moreover, I was immersed in learning about computer system 
architecture and operating systems while at EMC and Infinidat, where I was
immersed in system software development work that included designing new
algorithms and data structures.

Similarly, it appears that my background in databases would be
useful in this capacity. While at Northwestern University, I worked on an
object-oriented database as part of my thesis work. I am also conversant with
SQL.

Certainly, it is not just technical skills which I would bring to this role.
My background has allowed me to understand the benefits of leadership and
teamwork. It is undeniable, that I come to recognize that a willingness to
exchange new ideas is critical to development. This has been essential to my
analytical, problem-solving and decision-making skills. Indeed, these skills
were maximized when I took the initiative to design an SSD testing regime
called write-pressure testing. Armed with it, we tested several SSDs until
identifying an exceptional SSD from a tiny UK based company. As a result,
EMC Corporation became the first enterprise storage company to offer solid 
state disk storage. And I was honored with the EMC President's Award.

Thank you for your consideration.  I welcome the opportunity to answer any
questions you may have. 
\end{newlfm}
\end{document}
