\section{Work Experience}

\cventry{2/2016 - 3/2020}{Consultant Technologist}{Infinidat Inc.}{Waltham, MA}{Platform Research and Development}
{
%{\bfseries Responsibilities} Participate in the creation and updates of qualification and test procedures and content,
%and/or lead them
%for HDDs, SSDs, PCIe cards and Servers. Create low-level tools and tests for manufacturing and qualifications.
%Handle specific issues with the vendors like firmware bugs and suspected design issues.
%Monitor the industry for new technologies. Participate in vendor technology updates and design reviews.
%Participate in recurring calls with selected vendors.
%Participate in the internal design reviews and code reviews.
	\begin{itemize}
		\item Designed and implemented hardware qualification processes for the
			off-the-shelf hardware components used to manufacture the flagship
			product. Hardware included x86-based Servers, Fibre channel HBAs,
			SAS HBAs, Ethernet adapters, Hard disk drives, Solid-state drives
			and Infiniband HBAs. The development was done primarily in Python
			on a CentOS Linux platform. The code was maintained under GitLab.
		\item Participated in internal design and code reviews; engaged in
			recurring calls with selected vendors. Followed up specific issues 
			with vendors, including but not limited to, firmware bugs and
			suspected design issues.
		\item  Monitored the industry for new technologies.
		\item Advised the manufacturing division on Integration and Verification Testing (IVT).
	\end{itemize}
}
\cventry{4/2013 - 1/2016}{Consultant Technologist}{EMC Corporation}{Hopkinton, MA}{}
{
%{\bfseries Responsibilities}
%Represent own specific area of expertise as well as EMC's broader technical and business vision in analyzing technology
%trends over a three-to-five year time span for influence and impact on EMC products, strategy, and technology.
	\begin{itemize}
		\item Represented the EMC VMAX Division as SME for HDD/SSD to vendors
			and the rest of the organization.
		\item Designed an algorithm for scheduling I/Os to SSDs to improve
			their performance in a RAID configuration. (U.S. Patent 8,375,187)
		\item Designed a new data layout scheme for hard disk drives to improve
			their performance in a tiered storage system. (U.S. Patents 8,838,887 and 8,976,636)
			The scheme was implemented and tested using an I/O driver written
			in C/C++ on CentOS Linux platform using the sg device driver.
	\end{itemize}
}
\cventry{3/2012 - 4/2013}{Consulting Performance Engineer}{EMC Corporation}{Hopkinton, MA}
{Innovation and Systems Engineering, Enterprise Storage Division}
{
	\begin{itemize}
        \item Designed and implemented the {\em Disk Cloning Appliance} used for bulk
            replacement of faulty disks in a storage array. The appliance was
			developed in C++ under CentOS Linux and used GTK+ for the user
			interface.
		\item Developed a simulator to evaluate the proposed metadata paging
			scheme in EMC VMAX Storage System. The software was developed in
			C++ on a CentOS Linux platform.
	\end{itemize}
}
\cventry{12/2006 - 3/2012}{Principal Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Innovation and Systems
Engineering, Enterprise Storage Division}
{ 
	\begin{itemize}
		\item Designed and implemented the {\em Secure Erase Appliance for SSDs}
			for the {\em EMC certified secure erase service} as part of the
			launch of SSDs in the EMC storage products lineup. The appliance was
			developed in C++ under CentOS Linux and used GTK+ for the user
			interface.
		\item Member of the team that developed tiered storage software for
			EMC VMAX marketed under the brand name FAST v1. (U.S. Patents
			8,566,553 and 8,966,216)
		\item Designed the disk performance modeling module for tiered storage
			software for EMC VMAX marketed under the brand name FAST v2.
			(U.S. Patent 8,868,798)
	\end{itemize}
}
\cventry{12/2003 - 12/2006}{Principal Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Performance Research Group,
Symmetrix Business Unit}
{
	\begin{itemize}
		\item Was member of the team that designed the new cache management
			subsystem in the EMC Symmetrix Storage System. (U.S. Patent 7,177,853)
		\item Proposed, prototyped and evaluated modifications to the RAID data rebuild algorithm
			in the EMC Symmetrix Storage System to improve its performance when
			the storage system is under heavy load (U.S. patent 7,406,574) The
			development was done in C under a proprietary BSD-derived RTOS.
		\item Maintained Cache Simulator software that simulated the behavior of the 
			shared memory cache model used by the EMC Symmetrix/VMAX storage system.
			The software was originally written in C. Ported it to C++.
		\item Developed and maintained Hard Disk Simulator software that
			simulated the behavior of different hard disk drives used by the
			EMC Symmetrix/VMAX storage system. The software was written in C++.
	\end{itemize}
}
\cventry{8/2000 - 12/2003}{Senior Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Performance Research Group,
Symmetrix Business Unit}
%{{\bfseries Responsibilities}
%\begin{itemize}
%\item  Design/implement/maintain simulation software for various parts of EMC's storage system product
%\item  Design/simulate/implement/analyze performance improvements for EMC's storage system product
%\end{itemize}
%}
{
	\begin{itemize}
		\item Proposed, prototyped and evaluated changes to how the EMC Symmetrix Storage System manages dirty data.
			(U.S. patents 6,865,648 and 7,437,515) The development was done in
			C under a proprietary BSD-derived RTOS.
		\item Proposed, prototyped and evaluated a new algorithm in the EMC Symmetrix Storage System schedules read
			operations on disk drives in RAID-1 configuration. (U.S. patents
			6,865,648 and 7,437,515) The development was done in C under a
			proprietary BSD-derived RTOS.
		\item Proposed, prototyped and evaluated enhancement to the existing data pre-fetching algorithm
			in the EMC Symmetrix Storage System for the cases where workloads contain short bursts of 
			contiguous data accesses. (U.S. patent 6,721,870) The development
			was done in C under a proprietary BSD-derived RTOS.
		\item Prototyped and evaluated changes to the multi-LRU caching mechanism int the EMC Symmetrix Storage
			System to strike a better balance between the performance (retaining frequently accessed data) and the cost
			(memory accesses needed to retain data in the cache).
			(U.S. patent 6,715,039) The development was done in C under a
			proprietary BSD-derived RTOS.
	\end{itemize}
}
\cventry{9/1996 - 6/2000}{Research Assistant}{Department of Electrical and Computer Engineering}
{Northwestern University}{Evanston, IL}
{\begin{itemize}
	\item System administrator for an IBM SP2 and SGI Origin belonging to the 
		Center for Parallel and Distributed Computing at Northwestern University.
	\item Developed methods for efficient access to large objects in an object-oriented
		database running on a distributed memory parallel computer. The
		software was written in C++.
	\end{itemize}}
\cventry{10/1994 - 8/1996}{Research Assistant}{Department of Electrical and
Computer Engineering}{Syracuse University}{Syracuse, NY}
{Designed and evaluated a multi-threaded run-time library for parallel I/O that
separated the compute and I/O tasks in two separate threads of control. The
software was written in C.}
\cventry{2/1994 - 7/1994}{Software Engineer}{Datamatics Ltd.}{Mumbai, India}{}
{Worked on a document sharing system over WAN. The software was written in C.}
\cventry{2/1993 - 1/1994}{System Executive}{Spectrum Business Support Pvt. Ltd.}
{Mumbai, India}{}{Was member of a team that implemented a archive retrieval system.
Wrote the communication layer of the software that connected the server running
on a SUN system to the client PC over a telephone line. The software was
written in C.}

\section{Education}   
\cventry{1996--2000}{Doctor of Philosophy}{Northwestern University}{Evanston, IL}{}{Computer Engineering}
\cventry{1994--1996}{Master of Science}{Syracuse University}{Syracuse, NY}{}{Computer Engineering}
\cventry{1987--1991}{Bachelor of Engineering}{Savitribai Phule Pune University}{Pune, India}{}{Computer Engineering}
\section{Awards and Recognition}
\cventry{2008}{President's Award at EMC Corp.}{For innovations related to solid state drive technology.}{}{}{}


%% \begin{longtable}{p{ 90pt}p{299pt}r}
%% {\bf Work Experience} & {\bf Consultant Technologist} & {2/2016 - 3/2020}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Platform Research and Development} \\
%%                       & {\em Infinidat Inc., Waltham, MA} \\
%% \\
%%                       & {\bf Consultant Technologist} & {2/2015 - 1/2016}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em VMAX Systems Engineering} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Consultant Technologist} & {10/2014 - 2/2015}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Office of CTO, Core Technologies Division} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Consultant Technologist} & {4/2013 - 10/2014}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Office of Strategy and Technology, Enterprise and Mid-range Storage Division} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Consulting Performance Engineer} & {3/2012 - 4/2013}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Innovation and Systems Engineering, Enterprise Storage Division} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Principal Performance Engineer} & {12/2006 - 3/2012}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Innovation and Systems Engineering, Enterprise Storage Division} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Principal Performance Engineer} & {12/2003 - 12/2006}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Performance Research Group, Symmetrix Business Unit} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Senior Performance Engineer} & {8/2000 - 12/2003}\\
%%                       & \multicolumn{2}{p{4.5in}}{\em Performance Research Group, Symmetrix Business Unit} \\
%%                       & {\em EMC Corporation, Hopkinton, MA} \\
%% \\
%%                       & {\bf Intern} & {Summer 1998}\\
%%                       & {\em Bell Laboratories, Murray Hill, NJ} \\
%% \\
%% %                      & {\bf Software Engineer} & {2/1994 - 7/1994}\\
%% %                      & {\em Datamatics Ltd., Mumbai, India} \\
%% %\\
%% %                      & {\bf System Executive} & {2/1993 - 1/1994}\\
%% %                      & {\em Spectrum Business Support Pvt. Ltd., Mumbai, India} \\
%% %\\
%% %                      & {\bf Freelance Work} & {7/1991 - 1/1993}\\
%% %                      & {\em Shree Software Consultants, Pune, India} \\
%% %\\
%% {\bf Education}       & {\bf Doctor of Philosophy} & 2000\\
%%                       & {\em Computer Engineering} \\
%%                       & {Northwestern University, Evanston, IL} \\
%% \\
%%                       & {\bf Master of Science} & 1996\\
%%                       & {\em Computer Engineering} \\
%% 	              & {Syracuse University, Syracuse, NY} \\
%% \\
%%                       & {\bf Bachelor of Engineering} & 1991\\
%%                       & {\em Computer Engineering} \\
%% 	              & {University of Poona, India} \\
%% \\
%% {\bf Awards}         & {\bf President's Award at EMC Corp.} & 2008 \\
%%                      & \multicolumn{2}{p{3.35in}}{For innovations related to solid state drive technology.}\\
%% \\
%% \end{longtable}
