\documentclass[10pt,a4paper,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{black}
\nopagenumbers{}
\usepackage[scale=0.75]{geometry}
\include{contact}
\quote{}
\begin{document}
\makecvtitle

\section{Skills}
\cvitem{}{{\em Innovation} Propose and evaluate new ideas. Use simulation and/or advanced development for evaluation.}
\cvitem{}{{\em Cross-functional Communication} Effective communicator for representing the technical side in strategy discussions.}
\cvitem{}{{\em Technology Adoption} Evaluate new products and technologies. Propose innovative ways to incorporate the technology in products.}
\cvitem{}{{\em Rapid Prototyping and Development} Assist projects/groups with deploying innovative solutions. 
Provide finished product by active participation in design, development and test processes.}
\section{Accomplishments}
\cvitem {Drive Technology}
{\begin{itemize}
        \item {SME for drive technology for both EMC VMAX storage array and Infinidat's
        Infinibox storage array.  Worked with product and program management to drive the strategy.
    Represented both products in interactions with drive vendors.}
        \item {Was part of the team that introduced the first SSD in the Symmetrix product line. Introducing
        new methodology for assessing SSDs as the technology continues to evolve. Innovations around SSD
        usage in the product (U.S. patent 8,010,738 and 8,375,187).}
    \end{itemize}}
\cvitem {Storage System Firmware} {Evaluated and proposed changes to various parts of the EMC
        Symmetrix microcode.  Some ideas made fundamental changes to how the product works
	       (U.S. patents 6,865,648 and 7,437,515 and 6,954,833 and 7,177,853). Others were
           incremental improvements (U.S. patents 6,715,039 and 6,721,870 and 7,406,574 and 7,552,280).}
\cvitem {Appliance Design}
{\begin{itemize}
         \item {Designed and implemented the {\em Secure Erase Appliance for SSDs} as part of the launch of SSDs
         in the EMC storage products lineup. The appliance is used by the
         {\em EMC certified secure erase service} to decommission/re-purpose SSDs in the field.}
     \item  {Designed and implemented a {\em Disk Cloning Appliance} for bulk replacement of faulty
             disks in a storage array. The appliance allows the storage array to function normally while
             the drives are being replaced. 150 appliance instances were used to replace several hundred
             thousand drives in storage arrays across the globe in little over a year.}
\end{itemize}}
\begin{samepage}
\cvitem {Infinibox Platform Development} {Responsible for introducing new technology to Infinidat's
        Infinibox platform. Consulted on new technology in diverse areas like NVMe, NVMeOF, Fibre Channel,
    SAS, Infiniband, Ethernet, SSDs, HDDs, servers and power infrastructure.}
\end{samepage}
\cvitem {Infinibox Component Qualification} {Responsible for design and implementation of all 
        component qualification processes for the Infinibox platform. Oversaw the qualification process
    and provided recommendation to the upper management for formal component approval.}
\cvitem {Infinibox Manufacturing Processes} {Provided consultation about different aspects of IVT for
            Infinidat Inc. Did a complete design and implementation of the Fibre Channel Adapter Testing in
        Manufacturing.}
\section{Work Experience}
\cventry{2/2016 - 3/2020}{Consultant Technologist}{Infinidat Inc.}{Waltham, MA}{Platform Research and Development}{}
\cventry{2/2015 - 1/2016}{Consultant Technologist}{EMC Corporation}{Hopkinton, MA}{VMAX Systems Engineering}{}
\cventry{10/2014 - 2/2015}{Consultant Technologist}{EMC Corporation}{Hopkinton, MA}{Office of CTO}{Core Technologies Division}
\cventry{4/2013 - 10/2014}{Consultant Technologist}{EMC Corporation}{Hopkinton, MA}{Office of Strategy and Technology}{Enterprise and Mid-range Storage Division}
\cventry{3/2012 - 4/2013}{Consulting Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Innovation and Systems Engineering}{Enterprise Storage Division}
\cventry{12/2006 - 3/2012}{Principal Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Innovation and Systems Engineering}{Enterprise Storage Division}
\cventry{12/2003 - 12/2006}{Principal Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Performance Research Group}{Symmetrix Business Unit}
\cventry{8/2000 - 12/2003}{Senior Performance Engineer}{EMC Corporation}{Hopkinton, MA}{Performance Research Group}{Symmetrix Business Unit}
\section{Education}   
\cventry{1996--2000}{Doctor of Philosophy}{Northwestern University}{Evanston, IL}{}{Computer Engineering}
\cventry{1994--1996}{Master of Science}{Syracuse University}{Syracuse, NY}{}{Computer Engineering}
\cventry{1987--1991}{Bachelor of Engineering}{Savitribai Phule Pune University}{Pune, India}{}{Computer Engineering}
\section{Awards and Recognition}
\cventry{2008}{President's Award at EMC Corp.}{For innovations related to solid state drive technology.}{}{}{}
\end{document}
